Figure 2 and figure 2 supplementary material

### 2022-03-09 Figures/Figure2.Rmd
reorganize figures

```{r}
# Does the typical deconvolution scatterplot comparing true proportions to certain deconvolution estimates. Called inside scatterplot_wrapper
scatterplot_truevsestimate <- function(merged_data, x, y, title, color, x_lab = "", y_lab = ""){
    merged_data %>% dplyr::select(all_of(x),all_of(y)) %>%
    na.omit() -> to_plot

@@

  return(your_plot)
}

# This function returns the Lymphocytes, Macrophages and Neutrophils summarized
# of a given method/signature.
# Works inside of ridgeplot_parse. it takes:
# -  'deconv_data': contains the deconvolution data to index and summarize. 
#
# -  'signature dictionary': contains the exact names of the method
#                           (if it works with one signature) or the signature
#                           (if it works with multiple methods). 
#
# - iterator: string to subscript the signatures_dict with either signature
#             or methods names depending where is it called
#
# - prefix: string to leave just celltype names when substracted to the columns
#             of deconv_data of the specified method (or method + signature).
#
# - celltype: name of the celltype to sumarize "Lymphocites", "Macrophages" or "Neutrophils"

@@

    ct_subset = data %>%
      dplyr::select(matches(ct)) %>%
      dplyr::rename("H&E" = ct) %>%
      gather() %>%
      mutate(key = str_remove_all(key, paste(substring_remove, collapse = "|")),
             key=factor(key, levels=names(cor.ct.sorted)),
             method = as.factor(str_extract(key, "[^_]+")))
  adjust_x <- max(ct_subset$value)
  final_plot[[ct]] <- print(ggplot(ct_subset, aes(x = value, y = key, colour = method)) +
    geom_density_ridges2(jittered_points = TRUE, position = "raincloud", 
                         point_size = 0.25, point_alpha = 0.25, alpha = 0.7, rel_min_height = 0.005, point_color = "black") +
    theme_ridges() + ggtitle(ct) +
    annotate("text", x = adjust_x, y = 1:length(cor.ct.sorted), label = paste0("R = ",round(cor.ct.sorted, 2)), colour = "brown") +
    scale_x_continuous(limits = c(0, (adjust_x + adjust_x*0.2))) +
    scale_colour_manual(values = cols) +
     theme(axis.text.x = element_text(color = "black", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
          axis.text.y = element_text(color = "black", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
          axis.title.x = element_text(color = "black", size = 10, angle = 0, hjust = .5, vjust = 0, face = "plain"),
          axis.title.y = element_text(color = "black", size = 10, angle = 90, hjust = .5, vjust = .5, face = "plain"),
          plot.title = element_text(color = "black", size = 20)) +
    ylab("") + xlab("% of cell type"))
  }
  return(final_plot)
}

wrapper_ridgeplot <- function(deconv_data, true_estimates, cancer_abreviation){

@@

  # calculate correlations
 return(plot_ridgeplot(data_toplot))
}

wrapper_tpurity <- function(deconv_data, true_estimates, cancer_abreviation){
  true_estimates %>% dplyr::filter(Cancer_type == cancer_abreviation, CPE != "NaN") %>% 
    arrange(factor(Sample_ID, levels = Sample_ID))  -> true_subset_

  return(final_plot)
}

@@

# Figure
## A) Tumor Purity
```{r}
wrapper_tpurity(deconv_data = tcga_deconv,true_estimates = Aran_all_facs, cancer_abreviation = "LUAD")
```

>>>>

```{r}
################################################################################
# Does the typical deconvolution scatterplot comparing true proportions to certain deconvolution estimates. Called inside scatterplot_wrapper
scatterplot_truevsestimate <- function(merged_data, x, y, title, color, x_lab = "", y_lab = ""){
    merged_data %>% dplyr::select(all_of(x),all_of(y)) %>%
    na.omit() -> to_plot

@@

  return(your_plot)
}
################################################################################

################################################################################
wrapper_tpurity <- function(deconv_data, true_estimates, cancer_abreviation){
  true_estimates %>% dplyr::filter(Cancer_type == cancer_abreviation, CPE != "NaN") %>% 
    arrange(factor(Sample_ID, levels = Sample_ID))  -> true_subset_

  return(final_plot)
}
################################################################################

################################################################################
# This function returns the Lymphocytes, Macrophages and Neutrophils summarized
# of a given method/signature.
# Works inside of ridgeplot_parse. it takes:
# -  'deconv_data': contains the deconvolution data to index and summarize. 
#
# -  'signature dictionary': contains the exact names of the method
#                           (if it works with one signature) or the signature
#                           (if it works with multiple methods). 
#
# - iterator: string to subscript the signatures_dict with either signature
#             or methods names depending where is it called
#
# - prefix: string to leave just celltype names when substracted to the columns
#             of deconv_data of the specified method (or method + signature).
#
# - celltype: name of the celltype to sumarize "Lymphocites", "Macrophages" or "Neutrophils"

@@

    ct_subset = data %>%
      dplyr::select(matches(ct)) %>%
      dplyr::rename("H&E" = ct) %>%
      gather() %>%
      mutate(key = str_remove_all(key, paste(substring_remove, collapse = "|")),
             key=factor(key, levels=names(cor.ct.sorted)),
             method = as.factor(str_extract(key, "[^_]+")))
  adjust_x <- max(ct_subset$value)
  final_plot[[ct]] <- print(ggplot(ct_subset, aes(x = value, y = key, colour = method)) +
    geom_density_ridges2(jittered_points = TRUE, position = "raincloud", 
                         point_size = 0.25, point_alpha = 0.25, alpha = 0.7, rel_min_height = 0.005, point_color = "black") +
    theme_ridges() + ggtitle(ct) +
    annotate("text", x = adjust_x, y = 1:length(cor.ct.sorted), label = paste0("R = ",round(cor.ct.sorted, 2)), colour = "brown") +
    scale_x_continuous(limits = c(0, (adjust_x + adjust_x*0.2))) +
    scale_colour_manual(values = cols) +
     theme(axis.text.x = element_text(color = "black", size = 12, angle = 90, hjust = .5, vjust = .5, face = "plain"),
          axis.text.y = element_text(color = "black", size = 12, angle = 0, hjust = 1, vjust = 0, face = "plain"),  
          axis.title.x = element_text(color = "black", size = 10, angle = 0, hjust = .5, vjust = 0, face = "plain"),
          axis.title.y = element_text(color = "black", size = 10, angle = 90, hjust = .5, vjust = .5, face = "plain"),
          plot.title = element_text(color = "black", size = 20)) +
    ylab("") + xlab("% of cell type"))
  }
  return(final_plot)
}
################################################################################

################################################################################
wrapper_ridgeplot <- function(deconv_data, true_estimates, cancer_abreviation){

@@

  # calculate correlations
 return(plot_ridgeplot(data_toplot))
}
################################################################################
```

@@

# Figure
## A) Tumor Purity
```{r}
wrapper_tpurity(deconv_data = tcga_deconv,true_estimates = Aran_all_facs, estimate = , cancer_abreviation = "LUAD")
```
